---
title: "simulation"
author: "Luan Mengxiao"
date: 2023-11-02
output: github_document
---

Load key packages

```{r}
library(tidyverse)
```

Set seed for reproductivity

```{r}
set.seed(12345)
```

Here's a simulation function

```{r}
sim_mean_sd = function(n_obs, mu = 5, sigma = 1) {
  
  x = rnorm(n_obs, mean = mu, sd = sigma)
  
  tibble(
    mean = mean(x),
    sd = sd(x)
  )
}
```

Let's see what this does

```{r}
sim_mean_sd(n_obs = 30)
```

Let's iterate to see how this works under repeated sampling

```{r}
output = vector("list", length = 100)

for(i in 1:100){
  output[[i]] = sim_mean_sd(n_obs = 30)
}

sim_results = bind_rows(output)
sim_results |>
  ggplot(aes(x = mean)) +
  geom_density()

sim_results |>
  summarize(
    mu_hat = mean(mean),
    sd_hat = sd(mean))
```

use a map function

```{r}
sim_result_df = 
  expand_grid(
    sample_size = c(30, 60, 120, 240),
    iter = 1:1000
  ) |>
  mutate(estimate_df = map(sample_size, sim_mean_sd)) |>
  unnest(estimate_df)

sim_result_df |>
  mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)) |>
  ggplot(aes(x = sample_size, y = mean)) +
  geom_boxplot()
```

```{r, include = FALSE}
sim_mean_sd = function(n_obs, true_p = .9) {
  
  x = rbinom(n_obs, size = 1, prob = true_p)
  
  tibble(
    mean = mean(x),
    sd = sd(x)
  )
}
```

### SLR

Goal is to write a function that simulates data and then fits a regression; then repeat to look at the distribution of estimated coefficients.

```{r}
beta_0 = 2
beta_1 = 3

sim_data = 
  tibble(
    x = rnorm(n = 30, mean = 1, sd = 1),
    y = beta_0 + beta_1 * x + rnorm(30, mean = 0, sd = 1)
  )

ls_fit = lm(y ~ x, data = sim_data)
ls_fit

sim_data |>
  ggplot(aes(x = x, y = y)) +
  geom_point()
```

Let's wrap this in a functino

```{r}
sim_slr = function(n_obs, beta_0 = 2, beta_1 = 3){
  sim_data = 
  tibble(
    x = rnorm(n = n_obs, mean = 1, sd = 1),
    y = beta_0 + beta_1 * x + rnorm(n_obs, mean = 0, sd = 1)
  )

  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta_0_hat = coef(ls_fit)[1],
    beta_1_hat = coef(ls_fit)[2]
  )
}

sim_slr(n_obs = 30)
```

run this a whole bunch of times

```{r}
sim_results_df = 
  expand_grid(
    sample_size = 30,
    iter = 1:1000
  ) |>
  mutate(estimate_df = map(sample_size, sim_slr)) |>
  unnest()
```

Let's look at results

```{r}
sim_results_df |>
  summarize(
    mean_b0_hat = mean(beta_0_hat),
    mean_b1_hat = mean(beta_1_hat)
  )

sim_results_df |>
  ggplot(aes(x = beta_0_hat)) +
  geom_histogram()

sim_results_df |>
  ggplot(aes(x = beta_0_hat, y = beta_1_hat)) +
  geom_point()
```

