---
title: "writing functions"
author: "Luan Mengxiao"
date: 2023-10-26
output: github_document
---

```{r}
library(tidyverse)
library(rvest)
```

Set seed for reproducibility.

```{r}
set.seed(12345)
```

### Z score function

Z scores substract the mean and divide by the sd.

```{r}
x_vec = rnorm(20, mean = 5, sd = .3)
```

Compute Z scores for `x_vec`.

```{r}
(x_vec - mean(x_vec)) / sd(x_vec)
```

Write a function to do this.

```{r}
z_score = function(x) {
  if(!is.numeric(x)){
    stop("Argument should be numbers")
  } else if(length(x) < 2) {
    stop("You need at least 2 numbers to get z scores")
  }
  z = (x - mean(x)) / sd(x)
  z
}
```

Check that this works.

```{r}
z_score(x = x_vec)
```

Keep checking.

```{r, error = TRUE}
z_score(x = 3)
z_score(c("my", "name", "is", "jeff"))
z_score(c(TRUE, TRUE, FALSE, TRUE))
z_score(iris)
```

### Multiple outputs

Write a function that returns the mean and sd from a sample of numbers.

```{r}
mean_and_sd = function(x){
    if(!is.numeric(x)){
    stop("Argument should be numbers")
  } else if(length(x) < 2) {
    stop("You need at least 2 numbers to get z scores")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(mean = mean_x,
         sd = sd_x)
}
```

Double check if this works.

```{r}
mean_and_sd(x_vec)
```

### Start getting means and sds

```{r}
x_vec = rnorm(n = 30, mean = 5, sd = .5)

tibble(mean = mean(x_vec),
       sd = sd(x_vec))
```

Let's write a funtion that uses `n`, a true mean and true SD as inputs.

```{r}
sim_mean_sd = function(n_obs, mu = 5, sigma = 1) {
  x_vec = rnorm(n = n_obs, mean = mu, sd = sigma)

  tibble(mean = mean(x_vec),
         sd = sd(x_vec))
}

sim_mean_sd(n_obs = 30, mu = 5, sigma = .5)
sim_mean_sd(n_obs = 3000, mu = 5, sigma = .5)
sim_mean_sd(n_obs = 30)
sim_mean_sd(12, 24, 4)
sim_mean_sd(mu = 12, n_obs = 24, sigma = 4)
```

### LoTR words

```{r}
fellowship_ring = 
  readxl::read_excel("data/LotR_Words.xlsx", range = "B3:D6") |>
  mutate(movie = "fellowship_ring")

lotr_load_and_tidy = function(path = "data/LotR_Words.xlsx", cell_range, movie_name) {
  movie_df = readxl::read_excel(path, range = cell_range) |>
    mutate(movie = movie_name) |>
    janitor::clean_names() |>
    pivot_longer(
      female:male,
      names_to = "sex",
      values_to = "words"
    ) |>
    select(movie, everything())
  
  movie_df
}

lotf_df = 
  bind_rows(
    lotr_load_and_tidy(cell_range = "B3:D6", movie_name = "fellowship_ring"),
    lotr_load_and_tidy(cell_range = "F3:H6", movie_name = "two_towers"),
    lotr_load_and_tidy(cell_range = "J3:L6", movie_name = "return_king"))
```

### NSDUH

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)

data_marj = 
  nsduh_html |> 
  html_table() |> 
  nth(1) |>
  slice(-1) |> 
  select(-contains("P Value")) |>
  pivot_longer(
    -State,
    names_to = "age_year", 
    values_to = "percent") |>
  separate(age_year, into = c("age", "year"), sep = "\\(") |>
  mutate(
    year = str_replace(year, "\\)", ""),
    percent = str_replace(percent, "[a-c]$", ""),
    percent = as.numeric(percent)) |>
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))

data_marj
```

Try to write a quick function.

```{r}
nsduh_table <- function(html, table_number, outcome_name) {
  
  table = 
    html |> 
    html_table() |> 
    nth(table_number) |>
    slice(-1) |> 
    select(-contains("P Value")) |>
    pivot_longer(
      -State,
      names_to = "age_year", 
      values_to = "percent") |>
    separate(age_year, into = c("age", "year"), sep = "\\(") |>
    mutate(
      year = str_replace(year, "\\)", ""),
      percent = str_replace(percent, "[a-c]$", ""),
      percent = as.numeric(percent),
      outcome = outcome_name) |>
    filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
}

nsduh_table(nsduh_html, 1, "marj")

nsduh_results = 
  bind_rows(
    nsduh_table(nsduh_html, 1, "marj_one_year"),
    nsduh_table(nsduh_html, 4, "cocaine_one_year"),
    nsduh_table(nsduh_html, 5, "heroin_one_year")
  )
```
